
---
output:
    html_document:
        code_folding: hide 
---
<br>

#### The provided dataset

`assignment2 <- c(16, 18, 14, 22, 27, 17, 19, 17, 17, 22, 20, 22)`
```{r }
assignment2 <- c(16, 18, 14, 22, 27, 17, 19, 17, 17, 22, 20, 22)
```
<br>

#### The provided code

`myMean <- function(assignment2) { return( sum(assignment) / length(someData) )}`
```{r }
myMean <- function(assignment2) { 
    
    # commented out due to error:
    # return(sum(assignment)/length(someData)) 
    
    # corrected version:
    return(sum(assignment2)/length(assignment2))
    
}
#tested <- myMean(assignment2)
```
<br>

#### Discussion

The code as provided will ultimately cause two errors:

* <span style="color:red">Error in myMean(assignment2) : object 'assignment' not found</span>
* <span style="color:red">Error in myMean(assignment2) : object 'someData' not found</span>
<br>

The code is intended to calculate the average of the dataset through a 
user-defined function. The two errors indicate that the function is
attempting to access two unknown or undeclared variables:
`assignment` and `someData`. Both unknowns should be replaced with
the function's receiving argument: `assignment2`.
<br>

So, corrected...the function now reads:
<br><br>
`myMean <- function(assignment2) { return( sum(assignment2) / length(assignment2) )}`
<br><br>

The call `myMean(assignment2)` will return `myMean` as: **`r myMean(assignment2)`**.
<br>

Sanity check, the built-in `mean {base}` function call of `mean(assignment2)`
returns: **`r mean(assignment2)`**.
<br>


<br><br>
Reference: 

* Matloff, *The Art of R Programming*, section 1.3
<br><br>

### GitHub
Related file(s) can be found at <a href="https://github.com/eltownes/USF-LIS4370/tree/master/Module%202">Git Me</a>
<br><br>

