
---
output:
    html_document:
        code_folding: hide 
---
<br>

#### The provided dataset - raw

`freqRaw <- c( ".6",".3",".4",".4",".2",".6",".3",".4",".9",".2" )`  
`bpRaw <- c( "103","87","32","42","59","109","78","205","135","176" )`  
`visit_1Raw <- c( "bad","bad","bad","bad","good","good","good","good","NA","bad")`  
`visit_2Raw <- c( "low","low","high","high","low","low","high","high","high","high" )`  
`visit_3Raw <- c( "low","high","low","high","low","high","low","high","high","high" )`

Notes:

* freq is frequency in the last 12 months e.g. freq of
    .3 equals .3*12=4 visits during the last 12 months
* bp is blood pressure  
* visit_x indicates assessment number  
* visits need to be re-encoded for numeric designations:  
    * 0: good or low
    * 1: bad or high  

<br>

#### Transform

Let's transform the data from strings to numbers and re-encode the visits
using conditional statements and a loop within a function.

```{r warning=FALSE}
freqRaw <- c( ".6",".3",".4",".4",".2",".6",".3",".4",".9",".2" )
bpRaw <- c( "103","87","32","42","59","109","78","205","135","176" )
visit_1Raw <- c( "bad","bad","bad","bad","good","good","good","good","NA","bad")
visit_2Raw <- c( "low","low","high","high","low","low","high","high","high","high" )
visit_3Raw <- c( "low","high","low","high","low","high","low","high","high","high" )

freq <- as.numeric( freqRaw )
bp <- as.integer( bpRaw )

replaceOldNew <- function(vect,old1,new1,old2,new2){
    for (i in 1:length(vect)){
        if (vect[i]==old1) vect[i]=new1
        if (vect[i]==old2) vect[i]=new2
    }
    return ( as.numeric(vect) )
}

visit_1 <- replaceOldNew(visit_1Raw,"bad",1,"good",0)
visit_2 <- replaceOldNew(visit_2Raw,"low",0,"high",1)
visit_3 <- replaceOldNew(visit_3Raw,"low",0,"high",1)

df <- data.frame( freq,bp,visit_1,visit_2,visit_3 )
df

```
<br>

#### Quick EDA

Boxplot of bloodpressure and Histogram of patient visits last 12 months.

```{r }
par(mfrow=c(1,2))
boxplot( df$bp , main="Blood Pressure" )
hist( df$freq*12 , main="Visits" , xlab="Months" , ylab="Patients" )
```
<br>

A summary of blood pressure.
```{r }
summary( df$bp )
```
<br>

#### BPs & MDs Ratings

There appears to be more of an agreement when blood pressure readings are
in the mid-range. Per the histogram somewhere between 50 and 150 - this 
includes rounding considerations.

```{r }
total <- rowSums( cbind(df$visit_1,df$visit_2,df$visit_3), na.rm=TRUE )
df <- cbind(df,total)
hist( df$bp , main="BP Reading Congruence" , xlab="Blood Pressure" , ylab="Doctors"  )
```
<br>

A bin width of 10 creates the following histogram.

```{r }
hist( df$bp , breaks=10, main="BP Reading Congruence" , xlab="Blood Pressure" , ylab="Doctors"  )
```
<br>

<br><br>

### GitHub
Related file(s) can be found at <a href="https://github.com/eltownes/USF-LIS4370/tree/master/Module%204">Git Me</a>
<br><br>

