
---
output:
    html_document:
        code_folding: hide 
---
<br>

#### The provided data

`names <- c("Jeb", "Donald", "Ted", "Marco", "Carly", "Hillary", "Bernie")`  
`abcPoll <- c(4, 62, 51, 21, 2, 14, 15)`  
`cbsPoll <- c(12, 75, 43, 19, 1, 21, 19)`
```{r }
names <- c("Jeb", "Donald", "Ted", "Marco", "Carly", "Hillary", "Bernie" )
abcPoll <- c(4, 62, 51, 21, 2, 14, 15)
cbsPoll <- c(12, 75, 43, 19, 1, 21, 19)
```
<br>

#### The data.frame

`pollResult <- data.frame(names,abcPoll,cbsPoll)`
```{r }
pollResult <- data.frame(names,abcPoll,cbsPoll)
str(pollResult)
pollResult
```
<br>

#### Let's determine the rank order for `names`. There are two possibilities.
<br>

##### (1) Ranking: simple average

Caveat: potential issue.

```{r }
avgPolls <- (abcPoll+cbsPoll)*.5
pollResult <- cbind(pollResult,avgPolls)
pollResult[ order(-avgPolls), ]
colSums( pollResult[2:3] )
```
<br>

Here we see the ranking sorted by `avgPolls`.  
What is the issue? The `abcPoll` and the `cbsPoll` have different raw totals -
169 vs 190. Probably due to different polling methodologies. Now, looking
at this small dataset...probably not a big deal
but, it could pose problems with larger datasets.  
Let's consider a proportional perspective.  
<br>

##### (2) Ranking: proportional

As (1) above but using `prop.table` first. Kind of normalizing the data?  

```{r }
prop_abc <- prop.table(abcPoll)
prop_cbs <- prop.table(cbsPoll)
propFrame <- data.frame(names,prop_abc,prop_cbs)

avgProps <- (prop_abc+prop_cbs)*.5
propResult <- cbind(propFrame,avgProps)
propResult[ order(-avgProps), ]

colSums( propFrame[2:3] )
```
<br>

The `prop_abc` and `prop_cbs` should add to 1...good.  
<br>
In this case, there is no difference in ranking when using a simple average
versus a proportional ranking. Maybe something to be watchful for the next
time.

<br><br>

### GitHub
Related file(s) can be found at <a href="https://github.com/eltownes/USF-LIS4370/tree/master/Module%203">Git Me</a>
<br><br>

