
---
output:
    html_document:
        code_folding: hide 
---
<br>


### Set environment
```{r message=0, results='hide'}
env <- c("readr","tidyverse","lubridate","lattice","ggplot2")
lapply(env, library, character.only = 1)
```
<br>


### Load, clean, tidy, & inspect dataset - "TechStocks.csv"

```{r }
# read in data
stocks.tmp <- read_csv("TechStocks.csv", col_names = TRUE) %>%
    mutate(Day = t) %>%
    mutate(Date_chr = Date) %>%
    mutate(Date_lub = mdy(Date)) %>%
    select(Day,Date_chr,Date_lub,AAPL,GOOG,MSFT)

# pivot to tidy the data
stocks <- stocks.tmp %>%
    pivot_longer(cols=c("AAPL","GOOG","MSFT"),
                 names_to = "Symbol", values_to = "Price" )

# inspect the data
glimpse(stocks)
summary(stocks)
```
<br>

This is a dataset of AAPL, GOOG, and MSFT stock prices from 1 December 2015 
to 1 December 2017. A time-series plot will be appropriate here.  

`Date_chr` is the date as character type (imported).  
`Date_lub` is the date as lubridate type.

<br>

### Base graphics

Base graphics provides the basics of graphics in R.  
It is probably best used when exploring datasets as the call is
very simple - a call to `plot`.  

```{r }
# simple plot
plot(Price ~ Day, data=stocks)
```
<br>

This is quite messy because the data is plotted on the same chart and uses the
same price scale. Let's look at just AAPL.

```{r }
# filter then plot
stocks %>% filter(Symbol=="AAPL") %>%
    plot(Price ~ Day, data=.)
```
<br>

Base graphics can be enhanced but it takes more effort and parameters can 
appear a bit cryptic e.g. usage of `cex`, `yaxt`, or `las`. The workflow can 
also be awkward when comparing/creating related plots as in this case with 3 
tech stocks. Each plot must be rendered individually which can create charting
inconsistencies. Also, a legend will have to be manually created.  

Still, some simple enhancements can be made as shown below.

```{r }
# pipe stocks and build the plot
stocks %>% filter(Symbol=="AAPL") %>%
    plot(Price ~ Day, cex = 0.25, yaxt="none", data=., 
        main="AAPL", col.main="blue",
        xlab="Days (starts on 12-1-2015)", ylab="Price"
        )
axis(2, seq(0,200,25),las=2)
abline( lm(AAPL ~ Day, data=stocks.tmp) )
```
<br>


### Lattice

Lattice provides several high-level functions. The `xyplot` is one 
type and is great for time-series plots. A simply call to `xyplot` looks
very much like a call to `plot` but its default formatting is much better.

```{r }
# pipe and filter to plot
stocks %>% filter(Symbol=="AAPL") %>%
    xyplot(Price ~ Day, data=.)
```
<br>

Lattice makes it easy to do a comparison. **Key to note here is that 
`scales = "free"` has been set**. Without it we end with the same scaling 
problem as above. However, with 'free scales' **it could introduce a misleading interpretation**.

```{r }
# straight plot
xyplot(Price ~ Day | Symbol, cex = 0.25, data=stocks,
       group = Symbol,
       type = c("p", "smooth"),
       scales = "free",
       main="Stocks (on free scales)", col.main="blue",
        xlab="Days (starts on 12-1-2015)", ylab="Price"
       )
```
<br>


### GGPLOT2

GGPLOT uses the Grammar of Graphics approach which identifies 7 layers: 
data, aesthetics, geometries, facets, statistics, coordinates, and themes.
This provides a systematic way to create a visualization.

We'll plot the same 3 tech stocks but instead we'll plot NOT price but
instead the percentage increase since 1 December 2015. The result should be
similar to the side-by-side comparison above but now we'll compare
percentages and could provide for much fairer analysis.

```{r }
# create a cumulative percentage column
stocksPerc <- stocks %>%
    group_by(Symbol) %>%
    mutate(Perc = ((Price - Price[1]) / Price[1]) * 100) %>%
    ungroup()

# plotting
stocksPerc %>% ggplot( aes(x=Date_lub,y=Perc) ) + 
    ggtitle("Stocks (percent chart)") + xlab("") + ylab("Percent") +
    geom_point(size=0.5, col=if_else(stocksPerc$Perc<0,"red","green3") ) + 
    facet_wrap(~Symbol) +
    theme_light() +
    theme(plot.title = element_text(hjust = 0.5)) +
    theme(axis.text.x = element_text(angle = 45, vjust = 0.5, hjust=1)) +
    theme(axis.title.y = element_text(angle = 0, vjust = 0.5, hjust=1))
```
<br>


<br><br>

### GitHub
Related file(s) can be found at <a href="https://github.com/eltownes/USF-LIS4370/tree/master/Module%209">Git Me</a>
<br><br>

