
---
output:
    html_document:
        code_folding: hide 
---
<br>

#### The provided code with the 'deliberate' bug.

```{r class.source = 'fold-show', eval=FALSE}

tukey_multiple <- function(x) {
   outliers <- array(TRUE,dim=dim(x))
   for (j in 1:ncol(x))
    {
    outliers[,j] <- outliers[,j] && tukey.outlier(x[,j])
    }
outlier.vec <- vector(length=nrow(x))
    for (i in 1:nrow(x))
    { outlier.vec[i] <- all(outliers[i,]) } return(outlier.vec) }

```

The code will first throw the following error:

<span style="color:red">Error: unexpected symbol in:</span>  
<span style="color:red">"   for (i in 1:nrow(x))</span>  
<span style="color:red">    { outlier.vec[i] <- all(outliers[i,]) } return"</span>  

Often, the first step in debugging is to re-align or re-organize the code for
readability. In this case, the error stems from a formatting one. Specifically,
`return` should be placed on its own line and should stand by itself.  

The corrected code is shown below.

```{r class.source = 'fold-show'}

tukey_multiple <- function(x) {
    
    outliers <- array(TRUE,dim=dim(x))
    for (j in 1:ncol(x)){
        outliers[,j] <- outliers[,j] && tukey.outlier(x[,j])
    }

    outlier.vec <- vector(length=nrow(x))
    for (i in 1:nrow(x)){
        outlier.vec[i] <- all(outliers[i,])
    }
    return(outlier.vec)
}

```


<br><br>

### GitHub
Related file(s) can be found at <a href="https://github.com/eltownes/USF-LIS4370/tree/master/Module%2011">Git Me</a>
<br><br>

